Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Proof-of-Concept V}}

### 2014-05-06 Paper.tex
Add dec() API.
Receipt/Transaction confusion.

The validity is determined as:
\begin{equation}
\begin{array}[t]{rcl}
S(T) & \neq & \varnothing \quad \wedge \\
\boldsymbol{\sigma}[S(T)] & \neq & \varnothing \quad \wedge \\
T_n & = & \boldsymbol{\sigma}[S(T)]_n \quad \wedge \\
g_0 & \leq & T_g \quad \wedge \\ 
v_0 & \leq & \boldsymbol{\sigma}[S(T)]_b \\
T_l \leq {B_H}_l - \ell(B_\mathbf{T})_2
\end{array}
\end{equation}

Note the final condition; the sum of the transaction's gas limit, $T_l$, and the gas utilised in this block prior, given by $\ell(B_\mathbf{T})_2$, must be no greater than the block's \textbf{gasLimit}, ${B_H}_l$:

@@

The given \textbf{gasUsed} and \textbf{minGasLimit} must correspond faithfully to the transactions listed. In the case of ${B_H}_m$, the minimum gas limit, all transactions included in the transaction receipt must have a gas price, ${T_0}_p$, that is at least this value:
\begin{equation}
\forall_{T \in B_\mathbf{T}} T_p \geq {B_H}_m
\end{equation}

@@

Finally, we define $\Pi$ as the new state given the block reward function $\Omega$ applied to the final transaction's resultant state, $\ell(B_\mathbf{T})_1$:
\begin{equation}
\Pi(\boldsymbol{\sigma}, B) \equiv \Omega(B, \ell(B_\mathbf{T})_{\boldsymbol{\sigma}})
\end{equation}

@@

\begin{itemize}
\item \texttt{bin()}: Converts the string to binary format.
\item \texttt{pad(l)}: Converts the string to binary format (ready for data parameters) and pads with zeroes until it is of width \texttt{l}. Will pad to the left if the original string is numeric, or to the right if binary. If \texttt{l} is less than the width of the string, it is resized accordingly.
\item \texttt{pad(a, b)}: Converts the string to binary format (ready for data parameters) and pads with zeroes on the left size until it is of width \texttt{a}. Then pads with zeroes on the right side until it has grown to size \texttt{b}. If \texttt{b} is less hat the width of the string, it is resized accordingly.
\item \texttt{unbin()}: Converts the string from binary format to hex format.
\item \texttt{unpad()}: Converts the string from binary format to hex format, first removing any zeroes from the right side.
\end{itemize}

>>>>

The validity is determined as:
\begin{equation}
\begin{array}[t]{rcl}
S(T) & \neq & \varnothing \quad \wedge \\
\boldsymbol{\sigma}[S(T)] & \neq & \varnothing \quad \wedge \\
T_n & = & \boldsymbol{\sigma}[S(T)]_n \quad \wedge \\
g_0 & \leq & T_g \quad \wedge \\ 
v_0 & \leq & \boldsymbol{\sigma}[S(T)]_b \quad \wedge \\
T_l & \leq & {B_H}_l - \ell(B_\mathbf{R})_u
\end{array}
\end{equation}

Note the final condition; the sum of the transaction's gas limit, $T_l$, and the gas utilised in this block prior, given by $\ell(B_\mathbf{R})_u$, must be no greater than the block's \textbf{gasLimit}, ${B_H}_l$:

@@

The given \textbf{gasUsed} and \textbf{minGasLimit} must correspond faithfully to the transactions listed. In the case of ${B_H}_m$, the minimum gas limit, all transactions included in the transaction receipt must have a gas price, ${T_0}_p$, that is at least this value:
\begin{equation}
\forall \; T \in B_\mathbf{T}: T_p \geq {B_H}_m
\end{equation}

@@

Finally, we define $\Pi$ as the new state given the block reward function $\Omega$ applied to the final transaction's resultant state, $\ell(B_\mathbf{R})_{\boldsymbol{\sigma}}$:
\begin{equation}
\Pi(\boldsymbol{\sigma}, B) \equiv \Omega(B, \ell(B_\mathbf{R})_{\boldsymbol{\sigma}})
\end{equation}

@@

\begin{itemize}
\item \texttt{bin()}: Converts the string to binary format.
\item \texttt{pad(l)}: Converts the string to binary format (ready for data parameters) and pads with zeroes until it is of width \texttt{l}. Will pad to the left if the original string is numeric, or to the right if binary. If \texttt{l} is less than the width of the string, it is resized accordingly.
\item \texttt{pad(a, b)}: Converts the string to binary format (ready for data parameters) and pads with zeroes on the left size until it is of width \texttt{a}. Then pads with zeroes on the right side until it has grown to size \texttt{b}. If \texttt{b} is less hat the width of the string, it is resized accordingly.
\item \texttt{unbin()}: Converts the string from binary format to hex format.
\item \texttt{unpad()}: Converts the string from binary format to hex format, first removing any zeroes from the right side.
\item \texttt{dec()}: Converts the string to decimal format (typically from hex).
\end{itemize}
